Large Scale Structure Reconstruction with Short-Wavelength Modes

### 2019-10-09 paper/v1.tex
1

Notice \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in Einstein-de Sitter universe. Nonetheless when we actually do related calculation in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{pert1} and \ec{f2} throughout the whole work.\\

@@

We claim that generally correlation function of three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:

@@

$\vk_1$ and $\vk_2$ corresponds to two arbitrary short modes and $\vk_3$ arbitrary long mode. The above equation is true since in a real life survey, we can only measure this long-wavelength mode very limited times. Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.\\

@@

where we use the fact that $F_2$ is symmetric function. Finally we have:

>>>>

Notice \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in Einstein-de Sitter universe. Nonetheless when we actually do related calculations in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{pert1} and \ec{f2} throughout the whole work.\\

@@

\peikai{Need to rephrase (don't know how): We claim that generally correlation function of three Gaussian fields is non-zero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:

@@

$\vk_1$ and $\vk_2$ corresponds to two arbitrary short modes and $\vk_3$ arbitrary long mode. The above equation is true since in a real life survey, we can only measure this long-wavelength mode very limited times. Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.}\\

@@

where we use the fact that $F_2$ is a symmetric function. Finally we have:
